Understanding domestic abuse

### 2019-07-23 case_for_support_TM_hacked.tex

\begin{document}
\title{ESRC SDAI Application - Understanding domestic abuse using Big Data}
\date{}
\maketitle

@@

 These analyses will consist the first UK-based comprehensive quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes.

@@

These analyses will constitute the first extensive analysis of the neighbourhood-level predictors of domestic abuse within the UK. \AT{publication plan. fancy behav journals? Nature Human Behaviour, PNAS}

>>>>

\begin{document}
\title{Understanding domestic abuse}
\date{}
\maketitle

@@

 \section{Publication Plan}
 These analyses will consist the first UK-based comprehensive quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes. The resulting paper will be targetted at The Lancet Public Health, and Social Science and Medicine.

@@

These analyses will constitute the first extensive analysis of the neighbourhood-level predictors of domestic abuse within the UK. We envisage two articles. One will be focussed upon general behavioural theory and the effect of the environment. This will be targetted towards Nature Human Behaviour, and PNAS. THe other article will focus upon the impications for criminology and policing. The target journal will be Criminology.

 \AT{publication plan. fancy behav journals? Nature Human Behaviour, PNAS}
